\section{Introduction}

\subsection{Problem Domain}

Neural Networks are thriving in the modern society with software ranging from facial recognition to language translation augmenting humans day-to-day.
In this aspect, Machine Learning (ML) for chemical sciences gains more and more value and therefore is the focus of an increasing amount of research.
In consequence, an increasing amount of data regarding molecules are gathered and labeled, multiplying the amount of information that can be used to train ML models to help chemical discovery and molecule analysis to aid chemical discovery for drug development and molecule investigation.

To aid in the improvement of ML models, benchmarks have been developed.
A benchmark in a ML setting, is a site where models are compared against an accumulation of datasets, where the datasets are usually split into fixed training- and testing sets.
The benchmark around which this project will be largely revolving is MoleculeNet.
They tried a standardized approach for splitting their data, by creating more ways in which these datasets can be split, that can be applied to every dataset they have.

As the MoleculeNet paper was published in 2018, we try to find and use methods already used in other context but not in the paper.
We will set up a dataset-to-metric model for each benchmark using new tools in four areas: splitters, featurizers, deep learning, and transfer learning.
These results will be compared against the best-known results from MoleculeNet. While we may not be able to enhance the best-known results, we will formulate our accumulated knowledge for future exploration.

\subsection{Definitions}

A graph is a mathematical structure that consists of a set of vertices $V$ and a set of edges $E$.
Similarly a attributed graph is a mathematical structure that consists of a set of vertices and a set of edges, where each vertex and edge has an attribute, e.g. $A(V \bigcup E) \to \Sigma^*$.
While this basic definition does not specify any conditions on the attributes, it is possible to limit the attributes to a certain set of values.
Some graph machine learning methods require the attributes to be of certain types or to provide certain functionality.

\subsection{MoleculeNet}

TODO: add information on MoleculeNet and DeepChem framework
